intro

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/method.Rmd
prepared for submission
Figure 2 moved to end of doc
cross ref to suppl material deleted

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015] was used.
Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] was used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
Attentional control were assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).

@@

```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm. Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures. Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants. After, the discounting procedure took place. All three regulation strategies were compared pairwise. Before the last block, participants could decide which regulation strategy they wanted to reapply. Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale. Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
```

@@

Sample size calculation was done using *G\*Power*[@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues[-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aimed to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).

>>>>

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015] was used.
Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] was used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
Attentional control were assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see the supplementary material.

@@

@@

Sample size calculation was done using *G\*Power*[@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues[-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aimed to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
Detailed information on power calculation for each hypothesis can be found in the design table.
